Paper Report "MacroBase: Prioritizing Attention in Fast Data" \\ Big Data Storage and Processing Infrastructures

### 2019-03-19 paper-report.tex
hey

		\\\textbf{3. Streaming Explanation.} They state in the paper that individual attributes have enough characteristics to support counts. To count individual attributes frequent items the MDP uses a heavy-hitters sketch called Amortized Maintenance Counter (AMC). However MDP also needs to track combinations of attributes and, for that, they developed a combination of data structures: AMC for the frequent attributes and an adaptation of the CPS-Tree data structure to store frequent attributes. To sum up the whole explanation streaming process, when a data point arrives at this summarization operator, \textit{MacroBase} inserts each point's attributes into an AMC sketch, then inserts a subset of point's attributes into a tree that maintains a frequency descending order and when the window elapses, \textit{MacroBase} decays the count of the items and the counts in each node of the prefix tree, removes the attributes that are no longer above the support threshold and rearranges the prefix tree order.

@@

>>>>

		\\\textbf{3. Streaming Explanation.} They state in the paper that individual attributes have enough characteristics to support counts. To count individual attributes frequent items the MDP uses a heavy-hitters sketch called Amortized Maintenance Counter (AMC). However, MDP also needs to track combinations of attributes and, for that, they developed a combination of data structures: AMC for the frequent attributes and an adaptation of the CPS-Tree data structure to store frequent attributes. To sum up the whole explanation streaming process, when a data point arrives at this summarization operator, \textit{MacroBase} inserts each point's attributes into an AMC sketch, then inserts a subset of point's attributes into a tree that maintains a frequency descending order and when the window elapses, \textit{MacroBase} decays the count of the items and the counts in each node of the prefix tree, removes the attributes that are no longer above the support threshold and rearranges the prefix tree order.

@@

		In this part of the paper, the researches set a prototype server for \textit{MacroBase} and tested the solution and several characteristics of its design, comparing the results with other solutions if possible.
		\\\textbf{1. Result Quality.} In order to test the result quality of \textit{MacroBase} they performed several tests with different inputs conditions. With these tests they confirmed high quality results: It is able to identify correlated causes of outlying data for noise of 20\% or more, a magnitude which is likely rare in practice; it accurately identifies systematic abnormalities in real world data; the ADR approach makes MDP resilient to variable arrival dates; and they even tested \textit{MacroBase} in production with CMT, obtaining undiscovered results.
		\\\textbf{2. End-to-End Performance.} After testing performance of different \textit{MacroBase} phases on different data sets, arriving to the conclusion that the overhead of each component is data -and query- independent.
		\\\textbf{3. Microbenchmarks and comparison.} They tested the cardinality aware explanation efficiency compared to FP-Growth and they found out that while having same results, \textit{Micro Base} strategy was faster. They also evaluated AMC and compared it to other heavy-hitter sketchers. Specifically compared with SpaceSaving, AMC outperfomanced having more space consumption cost which may be a fact to take into account in case you must save memory space.
		\\\textbf{4. Case studies and extensibility.} Finally, in the tests explained in the paper they expose how they tested \textit{MacroBase} over supervised, time-based and video surveillance data, showing different application and successful results.
	\section{Conclusions}
